Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 PandaEvolution.tex
checkpoint.

Currently, very few HEP applications could benefit from Titan's GPUs but some
computationally-intensive and non memory-intensive tasks of ATLAS workflows can
be offloaded from the Grid to Titan's large amount of cores. Further, when HEP
tasks can be partitioned to independent jobs, Titan worker nodes can be used to
execute up to 16 concurrent payloads, one for each available core. Given these
constraints and challenges, the type of task most suitable for execution at the
moment on Titan is Monte Carlo detector simulation. This type of task is mostly
computational-intensive, requiring less than 2GB of RAM at runtime and with
small input data requirements. Detector simulation tasks in ATLAS account for
$\approx$ 60\% of all the jobs on WLCG, making them a primary candidate for
offloading.

>>>>

Currently, very few HEP applications can benefit from Titan's GPUs but some
computationally-intensive and non memory-intensive tasks of ATLAS workflows can
be offloaded from the Grid to Titan's large amount of cores. Further, when HEP
tasks can be partitioned to independent jobs, Titan worker nodes can be used to
execute up to 16 concurrent payloads, one for each available core. Given these
constraints and challenges, the type of task most suitable for execution at the
moment on Titan is Monte Carlo detector simulation. This type of task is mostly
computational-intensive, requiring less than 2GB of RAM at runtime and with
small input data requirements. Detector simulation tasks in ATLAS account for
$\approx$ 60\% of all the jobs on WLCG, making them a primary candidate for
offloading.
